### 2023-03-27 seitan/seitan.tex
more important changes

Among these, the last idea at least produces something both edible and texturally close to the crispy exterior the protagonist remembers, but it is only ``close'' like standing on the next tallest mountain peak and looking across the way at the one you {\em meant} to climb is ``close''.
Everything you say is touched by the spectre of health food writing,
because your reader must be into \textasciitilde{}vegan alternatives\textasciitilde{}.
Drowning in your million useless results the protagonist knows one truth deep in their heart: Seitan wings is not a health food.

@@

You are one of the first stops they make
(friends in tow, of course),
a high honor in the book of a foodie ex-grad-student who knows the East End inside and out.
They have practiced Chapter 2's secret lost art, but something is still wrong,
and sitting at your table in the summer heat they realize what it is:
technique aside, even fully cooked, their dough produces a chewy, glutinous inside,
whereas your wings are perfectly soft;
one's teeth pierce the fried shell and sink effortlessly through to the other side
in a delightful textural contrast.
They do not know how to replicate it, and at this point are too invested in the narrative to just ask.

@@

\chapter{4}{Tender}

@@

June being Pride month,
the protagonist's employer attempts some trans-themed programming,
% (new from the generic corporate rainbows they usually do),
but they dramatically neglect the ``nothing about us without us'' test
and commit several terrible faux pas.
Several trans employees complain in slack,
and the brass tone police them into silence.
One is nearly fired.
The protagonist, already having been silenced previously,
can only try to help behind the scenes,
and it's good they're traveling so they have someone to weakly say ``hold me'' to
while they work through their trauma response.
Like always in protests, the surface problems get fixed, and the rest are left to become scars in the sands of time -- almost as long as it takes to knead you.

With only a week in this visit, between all that and all the video games the humans need to nerd over, there isn't time to synthesize your wisdom into the main quest.
Instead they fry up slices of you, toss you in buffalo sauce (as if you need it),
and produce, speaking extremely charitably, a Scientific Byproduct.

@@

\chapter{5}{Synthesis}

@@

%It's the first time you've seen them since quarantine, and
You have a lot to catch up on.
Where there was border collie Louie, there is now border collie Junior.
You will never know if Louie could tell you smell different now.
You are teaching your mom to play Heaven's Vault,
your new favorite conlang-learning archaeology VN,
trying to tell her that the helplessness the game makes her feel is in fact diagetic,
and she (also a language nerd) is kinda actually getting it.
%
Your psychological association is still tenuous,
because your gender is new to them and your body is new to all three of you,
but your parents will get there someday, beyond the scope of this work.

@@

\noindent You acknowledge Will Scott, William Lovas, Rob Simmons, Chris Martens, Eve Blum, David Blum, and Jenny Lin for their invaluable roles in the story.

@@

\begin{center}
	% {\sc \Large ben blum's seitan wings}
	{\sc \Large trans rights seitan wings}
\end{center}

>>>>

Among these, the last idea at least produces something both edible and texturally close to the crispy exterior the protagonist remembers, but it is only ``close'' like standing on the next tallest mountain peak and looking across the way at the one you {\em meant} to climb is ``close''.
Everything you say is touched by the spectre of health food writing,
because your think your reader must be into \textasciitilde{}vegan alternatives\textasciitilde{}.
Drowning in your million useless faces the protagonist knows one truth deep in their heart: Seitan wings is not a health food.

@@

You are one of the first stops they make
(friends in tow, of course),
a high honor in the book of a foodie ex-grad-student who knows the East End inside and out.
They have practiced Chapter 2's secret lost art, but something is still wrong,
and sitting at your table in the summer heat they realize what it is:
technique aside, even fully cooked, their dough yields a chewy, glutinous inside,
whereas your insides are perfectly soft;
one's teeth pierce the fried shell and sink effortlessly through to the other side
in a delightful textural contrast.
They do not know how to replicate it, and at this point are too invested in the narrative to just ask.

@@

\chapter{4}{Tenderness}

@@

June being Pride month,
the protagonist's employer attempts some trans-themed programming,
% (new from the generic corporate rainbows they usually do),
but they dramatically neglect the ``nothing about us without us'' test
and commit several terrible faux pas.
Trans employees complain in slack,
and the brass tone police them into silence.
One is nearly fired.
The protagonist, already having been silenced previously,
can only try to help behind the scenes,
and it's good they're traveling so they have someone to weakly say ``hold me'' to
while they work through their trauma response.
Like always in protests, the surface problems get fixed, and the rest are left to become scars in the sands of time -- almost as long as it takes to knead you.

With only a week in this visit, between that and all the video games the humans need to nerd over, there isn't time to synthesize your wisdom into the main quest.
Instead they fry up slices of you, toss you in buffalo sauce (as if you need it),
and produce, speaking extremely charitably, a Scientific Byproduct.

@@

\chapter{5}{Wings}

@@

%It's the first time you've seen them since quarantine, and
You have a lot to catch up on.
Where there was border collie Louie, there is now border collie Junior.
You will never know if Louie could tell you smell different now.
You are teaching your mom to play Heaven's Vault,
your new favorite conlang-learning archaeology VN,
trying to tell her that the helplessness the game makes her feel is in fact diagetic,
and she (also a language nerd) is kinda actually getting it.
%
Your psychological association is still tenuous,
because your gender is new to them and your body is new to all three of you,
but your parents will get there later, beyond the scope of this work.

@@

\noindent You thank Ellen Scherb, Will Scott, William Lovas, Rob Simmons, Chris Martens, Eve Blum, David Blum, and Jenny Lin for their invaluable roles in the story.

@@

\begin{center}
	% {\sc \Large ben blum's seitan wings}
	% {\sc \Large trans rights seitan wings}
	{\sc \large Quarantine seitan wings}
\end{center}
